Online {\IterComp}

### 2017-11-16 results.tex
results

In this section we discuss our experimental evaluation of the work profiling strategies and 
the effectiveness of the work efficiency metric on guiding true online {\itercomp}.
We use the following naming convention for the profiling strategies considered
throughout this section:
\begin{itemize}[leftmargin=3mm]
\item \textbf{\OracleRM} measures the actual speedup over the unoptimized version of the program for any given input.
In our experiments, this oracle is allowed to execute each input at least twice so the speedup can be computed.
\item \textbf{\OraclePP} measures the work efficiency metric with a \textit{magically perfect} non-intrusive profiling.
  Because this version simulates a \textit{perfect} profiling, with zero overhead,
  it allows us to isolate and evaluate the actual effectiveness of the work efficiency metric.
\item \textbf{\OptProf} corresponds to the work profiling using the optimal placement of the probes.
  This profiling strategy requires a single execution of the program for any given input.
\item \textbf{\WCRelax-\textit{N}\%} measures the work efficiency metric using the work profiling with a \textit{N}\% threshold for
the \WCRelaxLower relaxation.
  Similar to the \OptProf, this profiling strategy also requires a single execution of the program for any given input.
\item \textbf{\WPRelax-\textit{N}\%} is similar to the \WCRelax, but it applies the \WPRelaxLower relaxation instead.
\end{itemize}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figs/speedups.pdf}
    \caption{Speedups obtained from the final optimization sequence selected by the online {\itercomp}.
	         The speedups reported for each benchmark represents the average speedup across their complete 1000 input datasets.}

    \FIXME{Sort  the bars according to speedup, i.e. Oracle should be the last bars.}
    \label{fig:speedups}
\end{figure*}

>>>>

In this section we discuss our experimental evaluation of the work profiling strategies and
the effectiveness of the work efficiency metric on guiding true online {\itercomp}.
We use the following naming convention for the profiling strategies considered
throughout this section:
\begin{itemize}[leftmargin=3mm]
\item \textbf{\OracleRM} measures the actual speedup over the unoptimized version of the program for any given input. In our experiments,
    this oracle is allowed to execute each input \emph{at least twice} so the speedup can be computed.
\item \textbf{\OraclePP} measures the work efficiency metric with a \textit{magically perfect} non-intrusive profiling.
  Because this version simulates a \textit{perfect} profiling, with zero overhead,
  it allows us to isolate and evaluate the actual effectiveness of the work efficiency metric.
\item \textbf{\OptProf} corresponds to the work profiling using the optimal placement of the probes. This profiling strategy requires
    \emph{a single execution} of the program for any given input.
\item \textbf{\WCRelax-\textit{N}\%} measures the work efficiency metric using the work profiling with a \textit{N}\% threshold for
the \WCRelaxLower relaxation.
  Similar to the \OptProf, this profiling strategy also requires a single execution of the program for any given input.
\item \textbf{\WPRelax-\textit{N}\%} is similar to the \WCRelax, but it applies the \WPRelaxLower relaxation instead.
\end{itemize}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figs/speedups.pdf}
    \caption{Speedups obtained from the final optimization sequence selected by the online {\itercomp}.
	         The speedups reported for each benchmark represents the average speedup across their complete 1000 input datasets.}
    \label{fig:speedups}
\end{figure*}
